Pangenome graph layout by Path-Guided Stochastic Gradient Descent

### 2024-04-19 manuscript/main.tex
update and PDFs files

\copyrightyear{2023} \pubyear{XXXX}

@@

	Software versions, code, and links to data resources used to prepare this manuscript can be found at \url{https://github.com/pangenome/sorting-paper}.
	Animations of the algorithm are deposited at \url{https://doi.org/10.5281/zenodo.8288999}.

@@

	%\clearpage
	%\setcounter{page}{1}

	%\beginsupplement

	%\section{Supplement}
	%
	% \subsection{Supplementary data}
	 %\subsection{Quantization} % DURING REVISION, IF NEEDED
	 %More details about your clever quantization.
	% \subsubsection{Performance evaluation}
	% \label{sec:performance}
	% The results of the performance evaluation are given in Table~\ref{tab:layout}.
	% \input{table_layout}
	 %\FIXME{What about the SMT thingy?} % DURING REVISION, IF NEEDED
	%\subsubsection{1D visualizations}	
	%The 1D PG-SGD algorithm creates a 1D layout of the nodes of the graph.
	%Theoretically, it is possible that 2 nodes have the same 1D coordinate or overlap.
	%But, in our 1D visualizations, we arrange the nodes from left to right.
	%Therefore, we project the 1D coordinates into a 1D node order: We sort the final layout by graph component, graph position, and node rank.
	%\input{fig_1d_sorts}

>>>>

\copyrightyear{2024} \pubyear{XXXX}

@@

	Software versions, code, and links to data used to prepare this manuscript can be found at \url{https://github.com/pangenome/sorting-paper}.
	Animations of the algorithm are deposited at \url{https://doi.org/10.5281/zenodo.8288999}.

@@

	\clearpage
	\setcounter{page}{1}

	\beginsupplement

	\section{Supplement}

	% \subsection{Supplementary data}
	 %\subsection{Quantization} % DURING REVISION, IF NEEDED
	 %More details about your clever quantization.
	\subsubsection{Performance evaluation}
	\label{sec:performance}
	The results of the performance evaluation are given in Table~\ref{tab:layout}.
	\input{table_layout}
	 %\FIXME{What about the SMT thingy?} % DURING REVISION, IF NEEDED
	\subsubsection{1D visualizations}	
	The 1D PG-SGD algorithm creates a 1D layout of the nodes of the graph.
	Theoretically, it is possible that 2 nodes have the same 1D coordinate or overlap.
	But, in our 1D visualizations, we arrange the nodes from left to right.
	Therefore, we project the 1D coordinates into a 1D node order: We sort the final layout by graph component, graph position, and node rank.
	\input{fig_1d_sorts}
